---
title: "Cliometrics Study Group"
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(cache = TRUE, message = FALSE, warning = FALSE, echo = FALSE)

library(tidyverse)
```

# Welcome!

This is the website of _Cliometrics Study Group_ organised by Economic History graduate students at the University of Tokyo.

Please note that the website is still under construction.


<!-- https://github.com/juba/rmdformats -->
  <!-- rmdformats::material: -->

# About the Study Group

*We love Economic History!!*

Holds a weekly meeting to read and discuss academic articles on economic history and applied microeconomics with historical data.


## Member

- [Erika IGARASHI](https://sites.google.com/view/erika-igarashis-website/%E3%83%9B%E3%83%BC%E3%83%A0)
- [Shuhei KAINUMA](https://kainume.github.io)


# Schedule

```{r table, echo=FALSE}
table <- tibble(Date = c("Dec. 25, 2020", "Dec. 30, 2020"),
                Paper = c("Becker, Rubin, and Woessmann (2020) WP", "Voth (2020) WP"))
table %>% 
 knitr::kable(format = 'html', digits = 3) %>% 
  kableExtra::kable_styling() 
```

# Papers Read in Our Meeting

# Useful Links

## Data Source

## Webinar

## Teaching Materials
