---
title: "Cliometrics Study Group"
css: custom.css
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(cache = TRUE, message = FALSE, warning = FALSE, echo = FALSE)

library(tidyverse)
```



# Welcome!

This is the website of _Cliometrics Study Group_ organised by Economic History graduate students at the University of Tokyo.

We hold a weekly meeting to read and discuss academic articles on economic history and applied microeconomics with historical data.  
Our current focus is on the interplay of culture and institutions in history.

<!-- Please note that the website is still under construction. -->


<!-- https://github.com/juba/rmdformats -->
  <!-- rmdformats::material: -->

<!-- # About the Study Group -->
<!-- # About Us -->

<!-- *We love Economic History!!* -->

## Member

- [Erika IGARASHI](https://sites.google.com/view/erika-igarashis-website/%E3%83%9B%E3%83%BC%E3%83%A0)
- [Shuhei KAINUMA](https://kainume.github.io)


# Schedule

```{r table_housekeeping, echo=FALSE, cache=TRUE}
link_url <- c("https://www.jstor.org/stable/j.ctt7zvbxt#:~:text=North%20argues%20that%20economic%20change,to%20political%20and%20economic%20feedback.",
              "https://www.jstor.org/stable/j.ctt7zvbxt#:~:text=North%20argues%20that%20economic%20change,to%20political%20and%20economic%20feedback.",
              "https://www.jstor.org/stable/j.ctt7zvbxt#:~:text=North%20argues%20that%20economic%20change,to%20political%20and%20economic%20feedback.",
              "https://www.jstor.org/stable/j.ctt7zvbxt#:~:text=North%20argues%20that%20economic%20change,to%20political%20and%20economic%20feedback.",
              "https://www.jstor.org/stable/j.ctt7zvbxt#:~:text=North%20argues%20that%20economic%20change,to%20political%20and%20economic%20feedback.",
              "https://www.jstor.org/stable/j.ctt7zvbxt#:~:text=North%20argues%20that%20economic%20change,to%20political%20and%20economic%20feedback.",
              "https://www.jstor.org/stable/j.ctt7zvbxt#:~:text=North%20argues%20that%20economic%20change,to%20political%20and%20economic%20feedback.",
              "https://s18798.pcdn.co/albertobisin/wp-content/uploads/sites/16384/2021/01/CI-HHEfin.pdf",
              "https://sites.google.com/site/pabloquerubin/research",
              "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=15795",
              "https://www.nber.org/papers/w27918",
              "https://www.nber.org/papers/w27852",
              "",
              "",
              "https://arxiv.org/abs/2102.00687",
              "https://www.nber.org/papers/w26410",
              "https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3680457",
              "https://www.nber.org/papers/w27706", 
              "https://www.nber.org/papers/w27706", 
              "https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3432796.",
              "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=15417",
              "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=14894", 
              "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=14894", 
              "https://economics.harvard.edu/files/economics/files/attitudesaptitudes.pdf", 
              "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=15208", 
              "https://www.nber.org/papers/w27967", 
              "https://www.nber.org/papers/w26754",
              "https://www.sciencedirect.com/science/article/pii/S0014498304000592", 
              "https://academic.oup.com/qje/article/123/3/1251/1928174?related-urls=yes&legid=qje;123/3/1251",
              "https://www.aeaweb.org/articles?id=10.1257/app.3.3.124",
              "https://academic.oup.com/qje/article/123/1/139/1889789",
              "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_42",
              "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_3",
              "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_33",
              "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_27",
              "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_23",
              "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_28",
              "http://www.yuhikaku.co.jp/books/detail/9784641164888"
              )
```

```{r table, echo=FALSE}
table <- tibble(Date = c("June 10th, 2021",
                         "June 3rd, 2021",
                         "May 27th, 2021",
                         "May 20th, 2021",
                         "May 14th, 2021",
                         "May 7, 2021",
                         "April 29, 2021",
                         "April 22, 2021",
                         "April 16, 2021",
                         "April 2, 2021",
                         "March 18, 2021",
                         "March 12, 2021",
                         "Feb. 26, 2021",
                         "Feb. 19, 2021",
                         "Feb. 12, 2021",
                         "Feb. 05, 2021",
                         "Jan. 29, 2021",
                         "Jan. 22, 2021",
                         "Jan. 15, 2021",
                         "Jan. 8, 2021",
                         "Dec. 30, 2020",
                         "Dec. 25, 2020",
                         "Dec. 18, 2020",
                         "Dec. 11, 2020",
                         "Dec. 04, 2020",
                         "Nov. 18, 2020",
                         "Nov. 11, 2020",
                         "Oct. 28, 2020",
                         "Oct. 21, 2020",
                         "Oct. 03, 2020",
                         "Sep. 26, 2020",
                         "Sep. 11, 2020",
                         "Sep. 04, 2020",
                         "Aug. 28, 2020",
                         "Aug. 20, 2020",
                         "Aug. 13, 2020",
                         "Aug. 06, 2020",
                         "From Apr. 10, 2020 to Jun. 28, 2020"
                         ),
                Paper = c("North (2005)\nUnderstanding the Process of Economic Change: Chap.11-13",
                          "North (2005)\nUnderstanding the Process of Economic Change: Chap.10",
                          "North (2005)\nUnderstanding the Process of Economic Change: Chap.8-9",
                          "North (2005)\nUnderstanding the Process of Economic Change: Chap.7",
                          "North (2005)\nUnderstanding the Process of Economic Change: Chap.5-6",
                          "North (2005)\nUnderstanding the Process of Economic Change: Chap.3-4",
                          "North (2005)\nUnderstanding the Process of Economic Change: Chap.1-2",
                          "Bisin & Verdier (2020) WP\nPhase Diagram in Historical Economics: Culture and Institution",
                          "Malis, Querubin, Satyanath (2020) WP\nPersistent Failure? International Interventions Since World War II",
                          "Bisin & Federico (2021) CEPR WP\nMerger or Acquisition ? Introduction to the Handbook of Historical Economics",
                          "Lowes (2020) NBER WP\nEthnographic and Field Data in Historical Economics",
                          "Acemoglu, Egorov, Sonin (2020) NBER WP\nInstitutional Change and Institutional Persistence",
                          "Research Presentation by Erika",
                          "Research Presentation by Shuhei",
                          "Ogasawara & Igarashi (2021) WP\nThe Impacts of the Gender Imbalance on Marriage and Birth: Evidence from World War II in Japan",
                          "Greenwood, Guner, Kopecky (2019) NBER WP\nThe Wife’s Protector: A Quantitative Theory Linking Contraceptive Technology with the Decline in Marriage",
                          "Persson & Tabellini (2020) WP\nCulture, Institutions and Policy",
                          "Nunn (2020) NBER WP (Cont.)",
                          "Nunn (2020) NBER WP\nHistory as Evolution",
                          "Yamasaki (2019) WP\nRailroads, Technology Adoption, and Modern Economic Development: Evidence from Japan",
                          "Voth (2020) CEPR WP\nPersistence - Myth and Mystery",
                          "Becker, Rubin, Woessmann (2020) CEPR WP (Cont.)",
                          "Becker, Rubin, Woessmann (2020) CEPR WP\nReligion in Economic History : A Survey",
                          "Mokyr (2019) WP\nAttitudes, Aptitudes, and the Roots of the Great Enrichment",
                          "Valencia Caicedo (2020) CEPR WP\nHistorical Econometrics: Instrumental Variables and Regression Discontinuity Designs",
                          "Giuliano & Matranga (2020) NBER WP\nHistorical Data: Where to Find Them, How to Use Them",
                          "Cantoni & Yuchtman (2020) NBER WP\nHistorical Natural Experiments: Bridging Economics and Economic History",
                          "Okazaki (2005) EEH\nThe role of the merchant coalition in pre-modern Japanese economic development: An historical institutional analysis",
                          "Qian (2008) QJE\nMissing Women and the Price of Tea in China: The Effect of Sex-Specific Earnings on Sex Imbalance",
                          "Abramitzky, Delavande, Vasconcelos (2011) AEJ: Applied\nMarrying up: The role of sex ratio in assortative matching",
                          "Nunn (2008) QJE\nThe long-term effects of Africa's slave trades",
                          "Hoffman (2019) Handbook of Cliometrics\nInstitutions",
                          "Diebolt & Perrin (2019) Handbook of Cliometrics\nCliometrics of Growth",
                          "Burnette (2019) Handbook of Cliometrics\nGender in Economic History",
                          "Margo (2019) Handbook of Cliometrics\nLabor Markets",
                          "Goldin (2019) Handbook of Cliometrics\nHuman Capital",
                          "Temin (2019) Handbook of Cliometrics\nEconomic History and Economic Development: New Economic History in Retrospect and Prospect",
                          "Sawai & Tanimoto (2016)\nThe Economic History of Japan: From the Early Modern Era to the Present"
                          )#,
                # Link = c("https://www.nber.org/papers/w26410",
                #          "https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3680457",
                #          "https://www.nber.org/papers/w27706",
                #          "https://www.nber.org/papers/w27706",
                #          "https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3432796.",
                #          "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=15417",
                #          "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=14894",
                #          "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=14894",
                #          "https://economics.harvard.edu/files/economics/files/attitudesaptitudes.pdf",
                #          "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=15208",
                #          "https://www.nber.org/papers/w27967",
                #          "https://www.nber.org/papers/w26754",
                #          "https://www.sciencedirect.com/science/article/pii/S0014498304000592",
                #          "https://academic.oup.com/qje/article/123/3/1251/1928174?related-urls=yes&legid=qje;123/3/1251",
                #          "https://www.aeaweb.org/articles?id=10.1257/app.3.3.124",
                #          "https://academic.oup.com/qje/article/123/1/139/1889789",
                #          "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_42",
                #          "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_3",
                #          "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_33",
                #          "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_27",
                #          "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_23",
                #          "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_28",
                #          "http://www.yuhikaku.co.jp/books/detail/9784641164888"
                #          )
                ) 
table %>% 
  mutate(Paper = kableExtra::cell_spec(Paper, 'html', link = link_url, color = 'green')) %>% 
  knitr::kable(format = 'html', digits = 3, escape = FALSE) %>% 
  # kableExtra::column_spec(1, width_min = "5em") %>% 
  # kableExtra::column_spec(2, width_min = "10em") %>% 
  # kableExtra::column_spec(3, width_min = "10em") %>% 
  kableExtra::row_spec(0, background = 'white') %>% # table header
  kableExtra::row_spec(seq(from = 2, to = nrow(table), by = 2), background = 'snow') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            bootstrap_options = c('striped', 'condensed', 'hover'))#c("hover", "condensed"))

```

<!-- # Papers Read in Our Meeting -->
# Papers Read

Mainly from

- [Handbook of Cliometrics vol.1 2nd edition(2019)](https://www.springer.com/gp/book/9783030001803)
- [Handbook of Historical Economics](https://www.elsevier.com/books/the-handbook-of-historical-economics/bisin/978-0-12-815874-6) (Working Paper Version)


<!-- # Useful Links -->

<!-- Coming soon! -->

<!-- ## Data Source -->

<!-- ## Webinar -->

<!-- ## Teaching Materials -->
