---
title: "Cliometrics Study Group"
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(cache = TRUE, message = FALSE, warning = FALSE, echo = FALSE)

library(tidyverse)
```

# Welcome!

This is the website of _Cliometrics Study Group_ organised by Economic History graduate students at the University of Tokyo.

Please note that the website is still under construction.


<!-- https://github.com/juba/rmdformats -->
  <!-- rmdformats::material: -->

# About the Study Group

<!-- *We love Economic History!!* -->

We hold a weekly meeting to read and discuss academic articles on economic history and applied microeconomics with historical data.


## Member

- [Erika IGARASHI](https://sites.google.com/view/erika-igarashis-website/%E3%83%9B%E3%83%BC%E3%83%A0)
- [Shuhei KAINUMA](https://kainume.github.io)


# Schedule

```{r table, echo=FALSE}
table <- tibble(Date = c("Dec. 25, 2020", 
                         "Dec. 30, 2020",
                         "Jan. 8, 2021",
                         "Jan. 15, 2021",
                         "Jan. 22, 2021",
                         "Jan. 29, 2021",
                         "Feb. 05, 2021"
                         ),
                Paper = c("Becker, Rubin, and Woessmann (2020) CEPR WP<br>Religion in Economic History : A Survey", 
                          "Voth (2020) CEPR WP<br>Persistence - Myth and Mystery",
                          "Yamasaki (2019) WP<br>Railroads, Technology Adoption, and Modern Economic Development: Evidence from Japan",
                          "Nunn (2020) NBER WP<br>History as Evolution",
                          "Nunn (2020) NBER WP (Cont.)",
                          "Persson & Tabellini (2020) WP<br>Culture, Institutions and Policy",
                          "Greenwood, Guner, Kopecky (2019) NBER WP<br>The Wife’s Protector: A Quantitative Theory Linking Contraceptive Technology with the Decline in Marriage"
                          ),
                Link = c("https://cepr.org/active/publications/discussion_papers/dp.php?dpno=14894",
                         "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=15417",
                         "https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3432796.",
                         "https://www.nber.org/papers/w27706",
                         "https://www.nber.org/papers/w27706",
                         "https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3680457",
                         "https://www.nber.org/papers/w26410"
                         )
                )
table %>% 
 knitr::kable(format = 'html', digits = 3, escape = FALSE) %>% 
  kableExtra::column_spec(1, width_min = "8em") %>% 
  kableExtra::column_spec(2, width_min = "10em") %>% 
  kableExtra::column_spec(3, width_min = "10em") %>% 
  kableExtra::kable_styling(full_width = F) 

```

<!-- # Papers Read in Our Meeting -->

# Useful Links

Coming soon!

<!-- ## Data Source -->

<!-- ## Webinar -->

<!-- ## Teaching Materials -->
