---
title: "Cliometrics Study Group"
css: custom.css
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(cache = TRUE, message = FALSE, warning = FALSE, echo = FALSE)

library(tidyverse)
```



# Welcome!

This is the website of _Cliometrics Study Group_ organised by Economic History graduate students at the University of Tokyo.

Please note that the website is still under construction.


<!-- https://github.com/juba/rmdformats -->
  <!-- rmdformats::material: -->

<!-- # About the Study Group -->
# About Us

<!-- *We love Economic History!!* -->

We hold a weekly meeting to read and discuss academic articles on economic history and applied microeconomics with historical data.


## Member

- [Erika IGARASHI](https://sites.google.com/view/erika-igarashis-website/%E3%83%9B%E3%83%BC%E3%83%A0)
- [Shuhei KAINUMA](https://kainume.github.io)


# Schedule

```{r table_housekeeping, echo=FALSE, cache=TRUE}
link_url <- c("https://arxiv.org/abs/2102.00687",
              "https://www.nber.org/papers/w26410",
              "https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3680457",
              "https://www.nber.org/papers/w27706", 
              "https://www.nber.org/papers/w27706", 
              "https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3432796.",
              "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=15417",
              "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=14894", 
              "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=14894", 
              "https://economics.harvard.edu/files/economics/files/attitudesaptitudes.pdf", 
              "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=15208", 
              "https://www.nber.org/papers/w27967", 
              "https://www.nber.org/papers/w26754",
              "https://www.sciencedirect.com/science/article/pii/S0014498304000592", 
              "https://academic.oup.com/qje/article/123/3/1251/1928174?related-urls=yes&legid=qje;123/3/1251",
              "https://www.aeaweb.org/articles?id=10.1257/app.3.3.124",
              "https://academic.oup.com/qje/article/123/1/139/1889789",
              "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_42",
              "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_3",
              "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_33",
              "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_27",
              "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_23",
              "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_28",
              "http://www.yuhikaku.co.jp/books/detail/9784641164888"
              )
```

```{r table, echo=FALSE}
table <- tibble(Date = c("Feb. 12, 2021",
                         "Feb. 05, 2021",
                         "Jan. 29, 2021",
                         "Jan. 22, 2021",
                         "Jan. 15, 2021",
                         "Jan. 8, 2021",
                         "Dec. 30, 2020",
                         "Dec. 25, 2020",
                         "Dec. 18, 2020",
                         "Dec. 11, 2020",
                         "Dec. 04, 2020",
                         "Nov. 18, 2020",
                         "Nov. 11, 2020",
                         "Oct. 28, 2020",
                         "Oct. 21, 2020",
                         "Oct. 03, 2020",
                         "Sep. 26, 2020",
                         "Sep. 11, 2020",
                         "Sep. 04, 2020",
                         "Aug. 28, 2020",
                         "Aug. 20, 2020",
                         "Aug. 13, 2020",
                         "Aug. 06, 2020",
                         "From Apr. 10, 2020 to Jun. 28, 2020"
                         ),
                Paper = c("Ogasawara & Igarashi (2021) WP\nThe Impacts of the Gender Imbalance on Marriage and Birth: Evidence from World War II in Japan",
                          "Greenwood, Guner, Kopecky (2019) NBER WP\nThe Wife’s Protector: A Quantitative Theory Linking Contraceptive Technology with the Decline in Marriage",
                          "Persson & Tabellini (2020) WP\nCulture, Institutions and Policy",
                          "Nunn (2020) NBER WP (Cont.)",
                          "Nunn (2020) NBER WP\nHistory as Evolution",
                          "Yamasaki (2019) WP\nRailroads, Technology Adoption, and Modern Economic Development: Evidence from Japan",
                          "Voth (2020) CEPR WP\nPersistence - Myth and Mystery",
                          "Becker, Rubin, and Woessmann (2020) CEPR WP (Cont.)",
                          "Becker, Rubin, and Woessmann (2020) CEPR WP\nReligion in Economic History : A Survey",
                          "Mokyr (2019) WP\nAttitudes, Aptitudes, and the Roots of the Great Enrichment",
                          "Valencia Caicedo (2020) CEPR WP\nHistorical Econometrics: Instrumental Variables and Regression Discontinuity Designs",
                          "Giuliano & Matranga (2020) NBER WP\nHistorical Data: Where to Find Them, How to Use Them",
                          "Cantoni & Yuchtman (2020) NBER WP\nHistorical Natural Experiments: Bridging Economics and Economic History",
                          "Okazaki (2005) EEH\nThe role of the merchant coalition in pre-modern Japanese economic development: An historical institutional analysis",
                          "Qian (2008) QJE\nMissing Women and the Price of Tea in China: The Effect of Sex-Specific Earnings on Sex Imbalance",
                          "Abramitzky, Delavande, Vasconcelos (2011) AEJ: Applied\nMarrying up: The role of sex ratio in assortative matching",
                          "Nunn (2008) QJE\nThe long-term effects of Africa's slave trades",
                          "Hoffman (2019) Handbook of Cliometrics\nInstitutions",
                          "Diebolt & Perrin (2019) Handbook of Cliometrics\nCliometrics of Growth",
                          "Burnette (2019) Handbook of Cliometrics\nGender in Economic History",
                          "Margo (2019) Handbook of Cliometrics\nLabor Markets",
                          "Goldin (2019) Handbook of Cliometrics\nHuman Capital",
                          "Temin (2019) Handbook of Cliometrics\nEconomic History and Economic Development: New Economic History in Retrospect and Prospect",
                          "Sawai & Tanimoto (2016)\nThe Economic History of Japan: From the Early Modern Era to the Present"
                          )#,
                # Link = c("https://www.nber.org/papers/w26410",
                #          "https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3680457",
                #          "https://www.nber.org/papers/w27706",
                #          "https://www.nber.org/papers/w27706",
                #          "https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3432796.",
                #          "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=15417",
                #          "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=14894",
                #          "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=14894",
                #          "https://economics.harvard.edu/files/economics/files/attitudesaptitudes.pdf",
                #          "https://cepr.org/active/publications/discussion_papers/dp.php?dpno=15208",
                #          "https://www.nber.org/papers/w27967",
                #          "https://www.nber.org/papers/w26754",
                #          "https://www.sciencedirect.com/science/article/pii/S0014498304000592",
                #          "https://academic.oup.com/qje/article/123/3/1251/1928174?related-urls=yes&legid=qje;123/3/1251",
                #          "https://www.aeaweb.org/articles?id=10.1257/app.3.3.124",
                #          "https://academic.oup.com/qje/article/123/1/139/1889789",
                #          "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_42",
                #          "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_3",
                #          "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_33",
                #          "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_27",
                #          "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_23",
                #          "https://link.springer.com/referenceworkentry/10.1007/978-3-030-00181-0_28",
                #          "http://www.yuhikaku.co.jp/books/detail/9784641164888"
                #          )
                ) 
table %>% 
  mutate(Paper = kableExtra::cell_spec(Paper, 'html', link = link_url, color = 'green')) %>% 
  knitr::kable(format = 'html', digits = 3, escape = FALSE) %>% 
  # kableExtra::column_spec(1, width_min = "5em") %>% 
  # kableExtra::column_spec(2, width_min = "10em") %>% 
  # kableExtra::column_spec(3, width_min = "10em") %>% 
  kableExtra::row_spec(0, background = 'white') %>% # table header
  kableExtra::row_spec(seq(from = 2, to = nrow(table), by = 2), background = 'snow') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            bootstrap_options = c('striped', 'condensed', 'hover'))#c("hover", "condensed"))

```

<!-- # Papers Read in Our Meeting -->
# Papers Read

- [Handbook of Cliometrics vol.1 2nd edition(2019)](https://www.springer.com/gp/book/9783030001803)
- Handbook of Historical Economics (Working Paper Version)


# Useful Links

Coming soon!

<!-- ## Data Source -->

<!-- ## Webinar -->

<!-- ## Teaching Materials -->
